Active Object Search with a Mobile Device for the Visually Impaired

### 2018-11-23 paper.tex

The reward function was hand-crafted and the parameters were empirically selected. The function values can be found in Table~\ref{tab:rewards}. The reward punishes the agent for every step it takes without finding the target object. The reward becomes more and more negatives as the agent progresses without finding the target~($n > n_{\max}$) or when it generates a waypoint in a location that was previously visited~($v = true$). Conversely, it gives a significant positive reward when the target object is found.

@@

The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes. A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the current the camera's orientation. Note that this cell is not part of the MDP' state: this radial grid is only used to discretised the pan-tilt movements of the camera and to guarantee a minimum angular variations between subsequent actions. The app's guidance system then uses the new waypoint's location to provide the user with guidance instructions. The grid is generated at the app's start-up and remains constant throughout the app's lifetime. The policy actions, and waypoints by extension, are given in relative to the user's current viewing pan/tilt position. The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.

>>>>

The reward function was hand-crafted and the parameters were empirically selected. The function values can be found in Table~\ref{tab:rewards}. The reward punishes the agent for every step it takes without finding the target object. The reward becomes more and more negatives as the agent progresses without finding the target~($n > n_{\max}$) or when it generates the same waypoint more than once~($v = true$) during the same search. Conversely, it gives a significant positive reward when the target object is found.

@@

The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes. A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the current the camera's orientation. Note that this cell is not part of the MDP' state: the radial grid is only used to discretise the pan-tilt movements of the camera and to guarantee a minimum angular variations between subsequent actions. The grid is generated at the app's start-up and remains constant throughout its lifetime. The app then uses the new waypoint's location to provide the user with guidance instructions. The policy actions, and waypoints by extension, are given relatively to the current camera's pan-tilt orientation. The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.
